THESIS PROJECT PROPOSAL

### 2019-11-08 project_ashish/paper.tex
commit

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 8}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
   \label{figure 8}
\end{figure}
